\documentclass[preview]{standalone}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{ragged2e}
\setlength\parindent{0pt}
\begin{document}
\begin{center}
\parbox{9cm}{\noindent{}\justifying{blah
Morton Brown and Robert Connelly, On graphs with a constant link, New Directions in the Theory of Graphs, Academic Press, 1973.

M. Burger and S. Mozes, Groups acting on trees: from local to global structure, Publications Mathématiques de l’IHÉS 92 (2000), no. 1, 113–150.

François Charton, Jordan S. Ellenberg, Adam Zsolt Wagner, and Geordie Williamson, Patternboost: Constructions in mathematics with a little help from ai, 2024.

Marcus Chijoff, Writing a GAP package for local action diagrams, 2023.

Marcus Chijoff and Stephan Tornier, Discrete (p)-closed groups acting on trees, 2024.

The GAP Group, GAP – Groups, Algorithms, and Programming, Ver- sion 4.8.7, 2017.

Yitzhak Katznelson, An introduction to harmonic analysis, Cambridge University Press, 1976.

B. Krön and R. Möller, Analogues of Cayley graphs for topological groups, Mathematische Zeitschrift 258 (2008), no. 3, 637.

Colin D. Reid and Simon M. Smith, Groups acting on trees with tits’ independence property (p), 2022.

J.-P. Serre, Trees, Springer, 1980.

S. Smith, A product for permutation groups and topological groups, Duke Mathematical Journal 166 (2017), no. 15, 2965–2999.

J. Tits, Sur le groupe des automorphismes d’un arbre, Essays on topology and related topics, Springer, 1970, pp. 188–211.

D. Van Dantzig, Zur topologischen Algebra. III. Brouwersche und Can- torsche Gruppen, Compositio Mathematica 3 (1936), 408–426 (de).  

George A Willis, The structure of totally disconnected locally compact groups, Mathematische Annalen 300 (1994), no. 1, 341–363.
9}}
\end{center}
\end{document}